NumPy---Array Programming in Python

### 2020-01-27 body.tex
Comment out 2nd example

Tools for analyzing data from gravitational wave observatories are
provided by the \code{pycbc} package, which was used in the first
detection of gravitational waves \cite{abbott2016observation} and in 
on-going analysis of data from LIGO and Virgo.
\code{pycbc} also make extensive use of the scientific Python ecosystem.
The time-series data from the interferometers are stored in NumPy arrays,
while the \code{scipy.signal} subpackage is used to construct and apply filters to the
data.
Matplotlib is used to visualize data at all points along the analysis chain
including raw data from the instrumentation and the time-frequency 
visualization of the ``chirps'' that result from mergers of compact binaries
such as black holes\cite{abbott2016observation} and
neutron stars\cite{abbott2017multi}.

>>>>

%Tools for analyzing data from gravitational wave observatories are
%provided by the \code{pycbc} package, which was used in the first
%detection of gravitational waves \cite{abbott2016observation} and in 
%on-going analysis of data from LIGO and Virgo.
%\code{pycbc} also make extensive use of the scientific Python ecosystem.
%The time-series data from the interferometers are stored in NumPy arrays,
%while the \code{scipy.signal} subpackage is used to construct and apply filters to the
%data.
%Matplotlib is used to visualize data at all points along the analysis chain
%including raw data from the instrumentation and the time-frequency 
%visualization of the ``chirps'' that result from mergers of compact binaries
%such as black holes\cite{abbott2016observation} and
%neutron stars\cite{abbott2017multi}.
